
```{r}
library(tidyverse)
library(here)
library(ggthemes)

#d <- read_csv(here("misc_data/stim_type_test.csv"))
scaled_d <- read_csv(here("misc_data/stim_type_rescaled.csv"))
scaled_d_fixed_animacy <- read_csv(here("misc_data/stim_type_fixanimacy.csv"))
scaled_d_fixed_schema_order <- read_csv(here("misc_data/stim_type_schema_order.csv"))
scaled_d_fixed_schema_unscaled <- read_csv(here("misc_data/stim_type_schema_order_unscaled.csv"))


cluster_scaled_d <- read_csv(here("misc_data/stim_type_replicate_cluster_smaller_distances.csv"))

#scaled_rep_d <- read_csv(here("misc_data/stim_type_replicate.csv"))
#scaled_rep_cluster_d <-  read_csv(here("misc_data/stim_type_replicate_cluster.csv"))
```

# unscaled stimuli
one stimuli pair per category, each pair runs 200 times

```{r}
d %>% 
  filter(`...1` == 5) %>% 
  ggplot(aes(x = v_type, y = sample_n)) + 
  #geom_point(position = position_jitter(width = .2)) + 
  stat_summary(fun.data = "mean_cl_boot") + 
  theme_few()
```
# scaled

one stimuli pair per category, each pair runs 200 times

```{r}
scaled_d_fixed_schema_unscaled %>% 
  filter(`...1` == 5) %>% 
  ggplot(aes(x = v_type, y = sample_n)) + 
  #geom_point(position = position_jitter(width = .2)) + 
  stat_summary(fun.data = "mean_cl_boot") + 
  theme_few()
```

```{r}
cluster_scaled_d %>% 
  filter(`...1` == 5) %>% 
  ggplot(aes(x = v_type, y = sample_n)) + 
  #geom_point(position = position_jitter(width = .2)) + 
  stat_summary(fun.data = "mean_cl_boot") + 
  theme_few() + 
  labs(title = "cluster run")
```

# scaled same parametrs

```{r}
scaled_d_fixed_animacy %>% 
  filter(`...1` == 5) %>% 
  ggplot(aes(x = v_type, y = sample_n)) + 
  #geom_point(position = position_jitter(width = .2)) + 
  stat_summary(fun.data = "mean_cl_boot") + 
  theme_few() + 
  labs(title = "local run")
```



these are teh

print(identity_fam, identity_test)
print(num_fam, num_test)
print(pose_fam, pose_test)
print(animacy_fam, animacy_test)

# unscaled embedding distance

```{r}
euclidean <- function(a, b) sqrt(sum((a - b)^2))

background_b <- c(0.4533, -0.9634, -0.7922)
background_d <- c( 0.4533, -0.9634, -0.7922)

identity_b <- c(  0.8621, -0.0764,  0.2498)
identity_d <- c(1.5216,  0.1411, -0.1434)

number_b <- c( -0.3219,  0.8121,  0.7056)
number_d <- c(-0.5816,  1.4219,  0.2670)

pose_b <- c(  1.8067, -0.2556, -0.6386)
pose_d <- c(1.6578, -0.1109, -0.7233)

animacy_b <- c(-1.3875, -1.4487,  0.0324)
#animacy_d <- c( 1.8204, -0.4493, -0.0524)
animacy_d <- c(  -0.4204, -1.4493, -0.0524)

eulidean_distance_df <- tibble(
  background_dist = euclidean(background_b, background_d), 
  identity_dist = euclidean(identity_b, identity_d), 
  number_dist = euclidean(number_b, number_d),
  pose_dist = euclidean(pose_b, pose_d), 
  animacy_dist = euclidean(animacy_b, animacy_d), 
  type = "euclidean"
)

sum_distance_df <- tibble(
  background_dist = sum(abs(background_b- background_d)),
  identity_dist = sum(abs(identity_b- identity_d)),
  number_dist = sum(abs(number_b- number_d)),
  pose_dist =  sum(abs(pose_b- pose_d)),
  animacy_dist =  sum(abs(animacy_b- animacy_d)),
  type = "sum"
)

bind_rows(
   eulidean_distance_df, 
   sum_distance_df
   
)

```
# scaled embedding distance

tensor([ 0.3558, -0.0828,  0.2068], dtype=torch.float64) tensor([ 0.3247, -0.0240,  0.2319], dtype=torch.float64)
tensor([ 0.2160, -0.0835,  0.0766], dtype=torch.float64) tensor([-0.1296, -0.0598,  0.0950], dtype=torch.float64)

```{r}
euclidean <- function(a, b) sqrt(sum((a - b)^2))

background_b <- c(-0.1407, -0.0929, -0.0746)
background_d <- c(-0.1407, -0.0929, -0.0746)

identity_b <- c(  0.2464,  0.2169, -0.1249)
identity_d <- c(0.2103,  0.1390, -0.1686)

number_b <- c( 0.1501,  0.1735, -0.0784)
number_d <- c( 0.1305,  0.0343, -0.1756)

pose_b <- c(  0.3558, -0.0828,  0.2068)
pose_d <- c( 0.3247, -0.0240,  0.2319)

animacy_b <- c( 0.2160, -0.0835,  0.0766)
#animacy_d <- c(  -0.1296, -0.0598,  0.0950)
animacy_d <- c(  0.1096, -0.0598,  0.0950)

eulidean_distance_df <- tibble(
  background_dist = euclidean(background_b, background_d), 
  identity_dist = euclidean(identity_b, identity_d), 
  number_dist = euclidean(number_b, number_d),
  pose_dist = euclidean(pose_b, pose_d), 
  animacy_dist = euclidean(animacy_b, animacy_d), 
  type = "euclidean"
)

sum_distance_df <- tibble(
  background_dist = sum(abs(background_b- background_d)),
  identity_dist = sum(abs(identity_b- identity_d)),
  number_dist = sum(abs(number_b- number_d)),
  pose_dist =  sum(abs(pose_b- pose_d)),
  animacy_dist =  sum(abs(animacy_b- animacy_d)),
  type = "sum"
)

bind_rows(
   eulidean_distance_df, 
   sum_distance_df
   
)
```

# artificial ones?!?

```{r}
euclidean <- function(a, b) sqrt(sum((a - b)^2))

background_b <- c(-0.1, -0.1, -0.1)
background_d <- c(-0.1, -0.1, -0.1)

identity_b <- c(-0.1, -0.1, -0.1)
identity_d <- c(0.2, 0.2, 0.2)

number_b <-  c(-0.1, -0.1, -0.1)
number_d <-  c(0.1, 0.1, 0.1)

pose_b <- c(-0.1, -0.1, -0.1)
pose_d <- c(0, 0, 0)

animacy_b <- c(-0.1, -0.1, -0.1)
#animacy_d <- c(  -0.1296, -0.0598,  0.0950)
animacy_d <- c(  0.3, 0.3,  0.3)

eulidean_distance_df <- tibble(
  background_dist = euclidean(background_b, background_d), 
  identity_dist = euclidean(identity_b, identity_d), 
  number_dist = euclidean(number_b, number_d),
  pose_dist = euclidean(pose_b, pose_d), 
  animacy_dist = euclidean(animacy_b, animacy_d), 
  type = "euclidean"
)

sum_distance_df <- tibble(
  background_dist = sum(abs(background_b- background_d)),
  identity_dist = sum(abs(identity_b- identity_d)),
  number_dist = sum(abs(number_b- number_d)),
  pose_dist =  sum(abs(pose_b- pose_d)),
  animacy_dist =  sum(abs(animacy_b- animacy_d)),
  type = "sum"
)

bind_rows(
   eulidean_distance_df, 
   sum_distance_df
   
)
```

# unscaled shcematic 

```{r}
euclidean <- function(a, b) sqrt(sum((a - b)^2))

background_b <- c(-1, -1, -1)
background_d <- c(-1, -1, -1)

identity_b <- c(-1, -1, -1)
identity_d <- c(2, 2, 2)

number_b <-  c(-1, -1, -1)
number_d <-  c(1, 1, 1)

pose_b <- c(-1, -1, -1)
pose_d <- c(0, 0, 0)

animacy_b <- c(-1, -1, -1)
#animacy_d <- c(  -0.1296, -0.0598,  0.0950)
animacy_d <- c( 3, 3, 3)

eulidean_distance_df <- tibble(
  background_dist = euclidean(background_b, background_d), 
  identity_dist = euclidean(identity_b, identity_d), 
  number_dist = euclidean(number_b, number_d),
  pose_dist = euclidean(pose_b, pose_d), 
  animacy_dist = euclidean(animacy_b, animacy_d), 
  type = "euclidean"
)

sum_distance_df <- tibble(
  background_dist = sum(abs(background_b- background_d)),
  identity_dist = sum(abs(identity_b- identity_d)),
  number_dist = sum(abs(number_b- number_d)),
  pose_dist =  sum(abs(pose_b- pose_d)),
  animacy_dist =  sum(abs(animacy_b- animacy_d)),
  type = "sum"
)

bind_rows(
   eulidean_distance_df, 
   sum_distance_df
   
)
```

## from cluster run? 

```{r}
scaled_rep_cluster_d %>% 
   filter(`...1` == 5) %>% 
  ggplot(aes(x = v_type, y = sample_n)) + 
  #geom_point(position = position_jitter(width = .2)) + 
  stat_summary(fun.data = "mean_cl_boot") + 
  theme_few()
```



```{r}
unscaled_embedding_range <- read_csv("/Users/caoanjie/Desktop/projects/RANCH/RANCH_cluster/sim_info/embeddings/resnet_pa.csv", col_names = FALSE) %>% 
  summarise(d1_max = max(X2), 
         d1_min = min(X2), 
         d2_max = max(X3), 
         d2_min = min(X3), 
         d3_max = max(X4), 
         d3_min = min(X4))

#embedding_range 
#grid_range
grid_range <- tibble(
  grid_max = -4,
  grid_min = 4
)

#embedding_interval (to what extent the eucledian distance matters? )
read_csv("/Users/caoanjie/Desktop/projects/RANCH/RANCH_cluster/sim_info/embeddings/resnet_pa.csv", col_names = FALSE)

#grid_interval
```

